Notes on generating initial models for mapping into {\tt MAESTRO}

### 2009-04-17 docs/initial_models/initial_models.tex
put the caption next to the figure so it takes less space
simplification to spherical initialization.  Before, we would fill rho, X, and p0 onto a multifab and then call the eos for h and T.  Since fill is just a piecewise constant operation, might as well use the base state h and T we already had.  Changes initial data by solver tolerance, but at least the code is doing the right thing now.

\subsection{Multilevel Plane-Parallel}
We do the same thing as the single-level case except that we generate
initial data at the non-finest levels by using linear interpolation
from the two nearest model points (see Figure \ref{Fig:Multilevel
  Initialization}).  Note that the initial data is not in HSE nor is
it thermodynamically consistent on non-finest cells.  We will enforce
these on the base state and full state later.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tpb]
\begin{center}
\epsffile{\figpath/multilevel_init.eps}
\caption{Multilevel Initialization.  The data from the initial model
  is represented by the dots on the right.  The initial data at the
  finest level is represented by the circles.  The initial data at
  non-finest levels is represented by the squares.  We copy data from
  the dots directly into the circles.  We use linear interpolation
  using the two nearest points to copy data from the dots to the
  squares.}
\label{Fig:Multilevel Initialization}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Given $p^{\init}, \rho^{\init}, T^{\init},$ and $X^{\init}$, this
section describes how the base state ($\rho_0$ and $p_0$) and full
state ($\rho, h, X$, and $T$) are computed.  We require that $\rho_0 =
\overline\rho$, the base state is in HSE according to equation
(\ref{HSE Discretization}), and the full state is thermodynamically
consistent with $p_0$.  Here are the steps:
\begin{enumerate}
\item For plane-parallel problems, fill $\rho^{\init}, h^{\init},
  X^{\init}$, and $T^{\init}$ onto a multifab to obtain the full state
  $\rho, h, X$, and $T$.  For spherical problems, fill $\rho^{\init},
  p^{\init}$, and $X^{\init}$ onto a multifab to obtain the full state
  $\rho, p$, and $X$, and then call the EOS to obtain the full state
  $h,T = h,T(\rho,p,X)$.  Note that this particular multifab version
  of $p$ is temporary, and can be deallocated after this step.
\item For spherical problems, skip the remaining steps and instead set
  $p_0 = p^{\init}$ and $\rho_0 = \rho^{\init}$.
\item If {\tt perturb\_model} = F, skip the remaining steps and
  instead set $p_0 = p^{\init}$ and $\rho_0 = \rho^{\init}$.
\item Perturb $T$, then compute $\rho,h = \rho,h(p^{\init},T,X)$.
\item Set $\rho_0 = \overline\rho$.
\item Compute $p_0$ using equation (\ref{HSE Discretization}), using
  the pressure at the top of the domain as the initial condition.
  Note that we still integrate upwards from the bottom, but then
  offset the final pressure so the pressure at the top of the domain
  remains unchanged.
\item Compute the full state $T,h = T,h(\rho,p_0,X)$.
\item Set $(\rho h)_0 = \overline{(\rho h)}$.
\end{enumerate}
Now $\rho_0 = \overline\rho$, the base state is in HSE, and the full
state is thermodynamically consistent with $p_0$.

>>>>

\subsection{Multilevel Plane-Parallel}
We do the same thing as the single-level case except that we generate
initial data at the non-finest levels by using linear interpolation
from the two nearest model points (see Figure \ref{Fig:Multilevel
  Initialization}).  Note that the initial data is not in HSE nor is
it thermodynamically consistent on non-finest cells.  We will enforce
these on the base state and full state later.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tpb]
\centering
\includegraphics[width=0.4in]{\figpath/multilevel_init}\hspace{0.2in}
\begin{minipage}[b]{5.0in}
\caption{Multilevel Initialization.  The data from the initial model
  is represented by the dots on the right.  The initial data at the
  finest level is represented by the circles.  The initial data at
  non-finest levels is represented by the squares.  We copy data from
  the dots directly into the circles.  We use linear interpolation
  using the two nearest points to copy data from the dots to the
  squares.\vspace{2em}}
\end{minipage}
\label{Fig:Multilevel Initialization}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Given $p^{\init}, \rho^{\init}, T^{\init},$ and $X^{\init}$, this
section describes how the base state ($\rho_0$ and $p_0$) and full
state ($\rho, h, X$, and $T$) are computed.  We require that $\rho_0 =
\overline\rho$, the base state is in HSE according to equation
(\ref{HSE Discretization}), and the full state is thermodynamically
consistent with $p_0$.  Here are the steps:
\begin{enumerate}
\item Fill $\rho^{\init}, h^{\init}, X^{\init}$, and $T^{\init}$ onto a 
  multifab to obtain the full state $\rho, h, X$, and $T$.
\item If {\tt perturb\_model} = F, skip the remaining steps and
  instead set $p_0 = p^{\init}$ and $\rho_0 = \rho^{\init}$.
\item Perturb $T$, then compute $\rho,h = \rho,h(p^{\init},T,X)$.
\item Set $\rho_0 = \overline\rho$.
\item Compute $p_0$ using equation (\ref{HSE Discretization}), using
  the $p^{\init}$ at the top of the domain as the one required boundary 
  condition.  Note that we still integrate upwards from the bottom, but then
  offset the final pressure so the pressure at the top of the domain
  remains unchanged.
\item Compute the full state $T,h = T,h(\rho,p_0,X)$.
\item Set $(\rho h)_0 = \overline{(\rho h)}$.
\end{enumerate}
Now $\rho_0 = \overline\rho$, the base state is in HSE, and the full
state is thermodynamically consistent with $p_0$.
